Evolutionary market ecologies \\ Model \& Numerical experiments

### 2021-06-07 draft.tex
Updates from Overleaf

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{url}
\usepackage{hyperref}
\newcommand{\code}{\texttt}
\usepackage[
backend=biber,
style=alphabetic,
sorting=ynt
]{biblatex}
\addbibresource{bibliography.bib}

@@

\begin{equation}
\label{excess_demand_equation}
   E_i(t) = \frac{W_i(t) {\lambda_i}}{p(t)} \left( \tanh{({c} \phi_i(t)}) + \frac{1}{2} \right) - S_i(t)
\end{equation}

@@

@@

This process allows to pin down the clearing price $p(t)$. We can thus compute the realised demands of the agents, update their asset shares ownership, wealth and profit. The agents receive dividends $D(t)$ in proportion of their asset shares, receive interest $r$ on their cash. Finally, investment inflows and outflows are modelled by the reinvestment parameter $f$, which is the multiplier of the agent profit, i.e. $W(t+1) - W(t)$. For $f > 1$, profits cause an inflow in capital. When $f < 1$, profits cause investors to withdraw funds from the agent-fund; finally, when $f=1$, no particular reinvestment dynamic occurs.

>>>>

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{url}
\usepackage{hyperref}
\newcommand{\code}{\texttt}
\usepackage[
backend=biber,
style=alphabetic,
sorting=ynt
]{biblatex}
\addbibresource{bibliography.bib}
\usepackage{amsmath}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}

@@

\begin{equation}
\label{excess_demand_equation}
   E_i(t, p(t)) = \frac{W_i(t) {\lambda_i}}{p(t)} \left( \tanh{({c} \phi_i(t)}) + \frac{1}{2} \right) - S_i(t)
\end{equation}

@@

Agent $i$'s wealth $W_i(t)$ evaluated at time $t$ is computed with:
\begin{equation}
    W_i(t) = C(t) + S(t)p(t) - L(t)
\end{equation}

@@

This process allows to pin down the clearing price $p(t)$. We can thus compute the realised demands of the agents, update their asset shares ownership, wealth and profit. The agents receive dividends $D(t)$ in proportion of their asset shares, receive interest $r$ on their cash. Finally, investment inflows and outflows are modelled by the reinvestment parameter $f$, which is the multiplier of the agent profit, i.e. $W(t+1) - W(t)$. For $f > 1$, profits cause an inflow in capital. When $f < 1$, profits cause investors to withdraw funds from the agent-fund; finally, when $f=1$, no particular reinvestment dynamic occurs. \\

Once the clearing price $p^* = \argmin \left(\sum_{a \in, \mathcal{A}} E_{a}(p)\right)^{2} $ has been determined, we update the inventories of the agents.
First, the number of asset shares the agents own is determined as:

\begin{equation}
    S_i(t+1) = E_i(t, p^*) + S_i(t)
\end{equation}

In general, the fixed supply constraint should hold for any $t$:

\begin{equation}
    \sum_i S_i(t) = Q
\end{equation}

The new cash is:

\begin{equation}
    C(t+1) = C(t) - (S(t+1) - S(t))p(t+1) - L(t+1) + L(t)
\end{equation}

Debt

% Debt is taken on when using leverage > 1 or leverage < -1. For long positions S(t) > 0 and we have L(t) = max(0, -(W(t-1) - S(t)p(t))). For short positions S(t) < 0, we have L(t) = max(0, -(W(t-1) + S(t)p(t))). From this, we should be able to buy W/p units without borrowing, and when short-selling we are restricted to short sell at most W/p units without borrowing. This is restricting the usage of the cash obtained from short-selling for something else (should we for example introduce more assets, we can not use the new cash to buy many other assets without violating leverage constraints).

% Margin M(t)  is something for the balance sheet only, it tracks the current value of the debt min(0, S(t))p(t). When you create the short position at time t, you sell some amount of stock for cash. This increases the pile of cash (see equation for C(t+1)), but it increases L(t) at the same time. Thus it would cancel out in the wealth equation.
